---
title: "BioImageOperation"
format: html
editor_options: 
  chunk_output_type: console
---

Analysis QMD for BioImageOperation output used in the larval crawling assay

## Environment

```{r}
library(tidyverse)
library(trajr)
library(qs)
library(skimr)
library(rstatix)
library(ggbeeswarm)
library(hrbrthemes)
library(patchwork)
library(ggpubr)
library(ggplot2)
library(ggforce)
library(viridis)
library(furrr)
library(colorspace)
`%!in%` = Negate(`%in%`)
```

## Prepare Analysis Dataframe

### Import raw 'Tracks' data from original repo - this code will not work without original repo

```{r}
# bio_output_dir <- "./OK6_gs2/Results/"
# bio_outputs <- list.files(bio_output_dir, pattern = ".csv", full.names = TRUE)
# 
# bio_raw <- future_map_dfr(bio_outputs, function(x){
#   filename <- basename(x)
#   tracks <- read_csv(x) %>%
#     mutate(filename = filename)
# })
# 
# bio_raw <- bio_raw %>%
#   mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label))
# 
# qsave(bio_raw %>% dplyr::select(-contour), "./OK6_gs2/Results/bio_raw.qs")

# bio_raw <- qread("./Mdr65/Results/bio_raw.qs")
```

### Filter for high confidence larvae

```{r}
# ## Filter for those tracked in the first 5 seconds 
# candidate_larvae1 <- bio_raw %>%
#   filter(time < 5) %>%
#   group_by(larva_id) %>%
#   summarise(frequency = n()) %>%
#   mutate(mean_frequency = mean(frequency)) %>%
#   filter(frequency >= mean_frequency) %>%
#   ungroup() %>%
#   pull(larva_id)
# 
# ## Filter for those that are flash-larvae
# candidate_larvae2 <- bio_raw %>%
#   filter(larva_id %in% candidate_larvae1) %>%
#   arrange(larva_id, time) %>%
#   group_by(larva_id) %>%
#   filter(cumsum(v >= 50) < 1) %>%
#   ungroup() %>%
#   pull(larva_id) %>% unique()
# 
# ## Take at most centre n number of larvae
# centre_x <- 470
# centre_y <- 350
# max_number_of_larvae <- 5
# 
# candidate_larvae3 <- bio_raw %>%
#   filter(larva_id %in% candidate_larvae1) %>%
#   filter(frame == 2) %>%
#   mutate(dist_from_centre = (centre_x - x)^2 + (centre_y - y)^2) %>%
#   group_by(filename) %>%
#   slice_min(dist_from_centre, n = max_number_of_larvae) %>%
#   ungroup() %>%
#   pull(larva_id) %>% unique()
# 
# ## Filter for those tracked for at least 2 seconds (e.g. 60 frames for 30 fps)
# candidate_larvae4 <- bio_raw %>%
#   filter(larva_id %in% candidate_larvae3) %>%
#   group_by(larva_id) %>%
#   summarise(frames = n()) %>%
#   ungroup() %>%
#   filter(frames >= 60) %>%
#   pull(larva_id) %>% unique()
# 
# ## Filter for abrupt decrease in area (removes the ones kept tracked even when the animal reaches the edge)
# min_area_threshold <- 75
# candidate_larvae5 <- bio_raw %>%
#   filter(larva_id %in% candidate_larvae4) %>%
#   arrange(larva_id, time) %>%
#   group_by(larva_id) %>%
#   filter(cumsum(area <= min_area_threshold) < 1) %>%
#   ungroup() %>%
#   pull(larva_id) %>% unique()
# 
# ## Filter for those that teleported & merged ones
# candidate_larvae6 <- bio_raw %>%
#   filter(larva_id %in% candidate_larvae5) %>%
#   arrange(larva_id, time) %>%
#   group_by(larva_id) %>%
#   mutate(Jumped = case_when(dist >= 5 ~ TRUE, TRUE ~ FALSE)) %>%
#   filter(cumsum(Jumped)<1) %>%
#   filter(!is_merged == TRUE) %>%
#   ungroup()
# 
# ##Filter for ones which crawl along the edge - stop tracking past some radius distance
# radius <- 310
# bio_within_radius <- candidate_larvae6 %>%
#   arrange(larva_id, time) %>%
#   group_by(larva_id) %>%
#   mutate("Distance_from_Centre" = sqrt((x - centre_x)^2 + (y - centre_y)^2)) %>%
#   mutate(Include = case_when(Distance_from_Centre >= radius ~ TRUE, TRUE ~ FALSE)) %>%
#   filter(cumsum(Include)<1) %>%
#   ungroup()
# 
# ## Filter for those tracked for too little frames
# candidate_larvae7 <- bio_within_radius %>%
#   group_by(larva_id) %>%
#   summarise(n = length(unique(time)))%>%
#   filter(n > 2) %>%
#   pull(larva_id) %>% unique()
# 
# ## Get confidence filtered dataframe
# bio_confident <- bio_within_radius %>%
#   filter(larva_id %in% candidate_larvae7) 
# 
# ## Check how many confident larvae were tracked per video 
# bio_confident %>%
#   group_by(filename) %>%
#   summarise(n = length(unique(track_label))) -> tmp1
# 
# to_remove <- c("OK6_CTRL6_larva_6", "OK6_CTRL7_larva_21", "OK6_CTRL7_larva_22", "OK6_GD4_larva_2", "OK6_KK4_larva_10")
# 
# # to_remove <- c("Nrv2_Control_8_larva_2", "Nrv2_lac_GD_7_larva_5", "Nrv2_lac_GD_8_larva_9", "Nrv2_lac_GD_8_larva_4")
# 
# # to_remove <- c("Mdr_control_3_larva_2", "Mdr_lac_GD_2_larva_15", "Mdr_lac_GD_2_larva_3")
# 
# bio_confident_after_removed <- bio_confident %>%
#   filter(!(larva_id %in% to_remove))
# 
# qsave(bio_confident_after_removed, "./OK6_gs2/Results/bio_confident_filtered.qs")
```

# START HERE TO REPRODUCE FROM DATA

# Read processed data

```{r}
bio_confident_after_removed <- qread("./Data/CH5_Crawling_assay_automated/Mdr65_bio_confident_filtered.qs")
```

### Perform analysis
```{r}
perform_analysis <- function(x){
  tracks_confident <- x
  
  mean_speed <- tracks_confident %>%
    filter(!is_merged == TRUE) %>%
  group_by(genotype, larva_id) %>%
  slice_max(dist_tot) %>%
  slice_max(time) %>%
  ungroup() %>%
  mutate(mean_speed = dist_tot/time) %>%
  dplyr::select(genotype, larva_id, mean_speed)
  
  index_straightness <- tracks_confident %>%
  group_by(genotype, larva_id) %>%
  filter(!is_merged == TRUE) %>%
  slice_max(dist_tot) %>%
  ungroup() %>%
  mutate(index_straightness = dist_origin/dist_tot) %>%
  dplyr::select(genotype, larva_id, index_straightness)
  
  get_trajDC <- function(x, y, time){
    tibble(x = x,
           y = y,
           time = time) %>%
      TrajFromCoords() %>%
      TrajSmoothSG(p = 1, n = 3) %>%
      TrajDirectionalChange() %>% 
      mean()
  }
  get_trajSDDC <- function(x, y, time){
    tibble(x = x,
           y = y,
           time = time) %>%
      TrajFromCoords() %>%
      TrajSmoothSG(p = 1, n = 3) %>%
      TrajDirectionalChange() %>% 
      sd()
  }
  
  DC <- tracks_confident %>%
    group_by(genotype, larva_id) %>%
    summarise(DC = get_trajDC(x, y, time),
              SDDC = get_trajSDDC(x, y, time))
  
  output <- full_join(mean_speed, index_straightness, by = c("genotype", "larva_id")) %>%
    full_join(DC, by = c("genotype", "larva_id")) %>%
    return()
}

# OK6
# bio_confident_anno <- bio_confident_after_removed %>%
#   mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
#   mutate(genotype = case_when(
#     str_detect(larva_id, "OK6") & str_detect(larva_id, "CTRL") ~ "OK6-GAL4 Control",
#     str_detect(larva_id, "OK6") & str_detect(larva_id, "GD") ~ "OK6-GAL4 > Lac RNAi",
#     str_detect(larva_id, "OK6") & str_detect(larva_id, "KK") ~ "OK6 KK",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "Control") ~ "Repo-GAL4 Control",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "GD") ~ "Repo-GAL4 > Lac RNAi"
#   )) %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   filter(genotype != "OK6 KK")
# 
# bio_summary <- perform_analysis(bio_confident_anno) %>%
#   distinct() %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   mutate(mean_speed_real_units = mean_speed * 85/650)

# Nrv2
# bio_confident_anno <- bio_confident_after_removed %>%
#   mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
#   mutate(genotype = case_when(
#     str_detect(larva_id, "Nrv2") & str_detect(larva_id, "Control") ~ "Nrv2-GAL4 Control",
#     str_detect(larva_id, "Nrv2") & str_detect(larva_id, "GD") ~ "Nrv2-GAL4 > Lac RNAi",
#     str_detect(larva_id, "Nrv2") & str_detect(larva_id, "KK") ~ "Nrv2 KK",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "Control") ~ "Repo-GAL4 Control",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "GD") ~ "Repo-GAL4 > Lac RNAi"
#   )) %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   filter(genotype != "Nrv2 KK")
# 
# bio_summary <- perform_analysis(bio_confident_anno) %>%
#   distinct() %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   mutate(mean_speed_real_units = mean_speed * 85/1000)

# Mdr65 
# bio_confident_anno <- bio_confident_after_removed %>%
#   mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
#   mutate(genotype = case_when(
#     str_detect(larva_id, "Mdr") & str_detect(larva_id, "control") ~ "Mdr65-GAL4 Control",
#     str_detect(larva_id, "Mdr") & str_detect(larva_id, "GD") ~ "Mdr65-GAL4 > Lac RNAi",
#     str_detect(larva_id, "Mdr") & str_detect(larva_id, "KK") ~ "Mdr65 KK",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "control") ~ "Repo-GAL4 Control",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "GD") ~ "Repo-GAL4 > Lac RNAi"
#   )) %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   filter(genotype != "Mdr65 KK")
# 
# bio_summary <- perform_analysis(bio_confident_anno) %>%
#   distinct() %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   mutate(mean_speed_real_units = mean_speed * 85/650)

# 46F
# bio_confident_anno <- bio_confident_after_removed %>%
#   mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
#   mutate(genotype = case_when(
#     str_detect(larva_id, "46F") & str_detect(larva_id, "control") ~ "46F-GAL4 Control",
#     str_detect(larva_id, "46F") & str_detect(larva_id, "GD") ~ "46F-GAL4 > Lac RNAi",
#     str_detect(larva_id, "46F") & str_detect(larva_id, "KK") ~ "46F KK",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "control") ~ "Repo-GAL4 Control",
#     str_detect(larva_id, "Repo") & str_detect(larva_id, "GD") ~ "Repo-GAL4 > Lac RNAi"
#   )) %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   filter(genotype != "46F KK")
# 
# bio_summary <- perform_analysis(bio_confident_anno) %>%
#   distinct() %>%
#   mutate(replicate = str_extract(larva_id, "\\d")) %>%
#   mutate(mean_speed_real_units = mean_speed * 85/1950)

# bio_summary %>%
#   group_by(genotype) %>%
#   summarise(n = n()) %>%
#   arrange(desc(n))
```

## Create summary and perform stats - individual subtype
```{r}
variables <- c("mean_speed_real_units", "index_straightness", "DC", "SDDC")

results <- map(variables, function(var) {
  
  # Check normality
  norm_result <- bio_summary %>%
    group_by(genotype) %>%
    shapiro_test(!!sym(var)) %>%
    add_significance()
  
  # Print
  print(norm_result)
  
  # Kruskal-Wallis test
  kw_result <- bio_summary %>%
    kruskal_test(reformulate('genotype', response = var))
  
  # Print
  print(kw_result)
  
  # Dunn test
  dunn_results <- bio_summary %>%
    dunn_test(reformulate('genotype', response = var)) %>%
    add_significance() %>% 
    as_tibble()
})

# Combine results
final_results <- bind_rows(results)

write.csv(final_results, "./Output/Crawling_assay_automated/statistical_results_14092023_OK6_crawling.csv", row.names = FALSE)
```

## Set stat comparisons
```{r}
# OK6
# stat_comparisons <- list(
#   c("OK6-GAL4 Control", "OK6-GAL4 > Lac RNAi")
# )

# Nrv2
# stat_comparisons <- list(
#   c("Repo-GAL4 Control", "Repo-GAL4 > Lac RNAi"),
#   c("Repo-GAL4 Control", "Nrv2-GAL4 Control"),
#   c("Nrv2-GAL4 Control", "Nrv2-GAL4 > Lac RNAi")
# )

# Mdr65
stat_comparisons <- list(
  c("Repo-GAL4 Control", "Repo-GAL4 > Lac RNAi"),
  c("Repo-GAL4 Control", "Mdr65-GAL4 Control"),
  c("Mdr65-GAL4 Control", "Mdr65-GAL4 > Lac RNAi")
)

# # 46F 
# stat_comparisons <- list(
#   c("Repo-GAL4 Control", "Repo-GAL4 > Lac RNAi"),
#   c("Repo-GAL4 Control", "46F-GAL4 Control"),
#   c("46F-GAL4 Control", "46F-GAL4 > Lac RNAi")
# )
```

## Plot analysis to PDF - individual subtype
```{r}
things_to_plot <- c("mean_speed_real_units", "index_straightness", "DC", "SDDC") %>% set_names()

colors <- viridisLite::inferno(6)

# Exclude the undesired color
colors <- colors[colors != "#FCFFA4FF"]
colors <- colors[colors != "#000004FF"]

# Define the desired order Nrv2
# ordered_levels <- c("OK6-GAL4 Control", "OK6-GAL4 > Lac RNAi")

# Define the desired order Nrv2
# ordered_levels <- c("Repo-GAL4 Control", "Repo-GAL4 > Lac RNAi", "Nrv2-GAL4 Control", "Nrv2-GAL4 > Lac RNAi")

# Define the desired order Mdr65
ordered_levels <- c("Repo-GAL4 Control", "Repo-GAL4 > Lac RNAi", "Mdr65-GAL4 Control", "Mdr65-GAL4 > Lac RNAi")

# Define the desired order 46F
# ordered_levels <- c("Repo-GAL4 Control", "Repo-GAL4 > Lac RNAi", "46F-GAL4 Control", "46F-GAL4 > Lac RNAi")

bio_summary <- bio_summary %>%
  mutate(genotype = factor(genotype, levels = ordered_levels))


pdf("./Output/Plots/CH5_16092023_Mdr65_analysis_crawling_parameters.pdf", width = 7, height = 5)
map(things_to_plot, ~ bio_summary %>%
  ggplot(aes_string(x = "genotype", y = .x, fill = "genotype")) + 
  geom_violin(color = 'NA', alpha = 0.2, trim = TRUE, scale = "width") +
  geom_quasirandom(width = 0.25, alpha = 0.9, size = 2, stroke = 0) +
  scale_fill_manual(values = colors) +
  labs(title = .x,
       x = "",
       y = "Measure") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none") + 
  stat_compare_means(comparisons = stat_comparisons, method = "wilcox.test", label = "p.signif") +
  geom_pointrange(stat = "summary", colour = "#C53270", size = 0.5))

dev.off()
```

#Plot all tracks to pdf
```{r}
centre_x <- 470
centre_y <- 350
radius = 320


# Create a dataframe with circle attributes
df <- data.frame(
  centre_x = centre_x,
  centre_y = centre_y,
  radius = radius
  )

# OK6
bio_confident_anno$genotype <- factor(bio_confident_anno$genotype,
                                      levels = c("OK6-GAL4 Control",
                                                 "OK6-GAL4 > Lac RNAi"))

# Mdr65
# bio_confident_anno$genotype <- factor(bio_confident_anno$genotype,
#                                       levels = c("Repo-GAL4 Control",
#                                                  "Repo-GAL4 > Lac RNAi",
#                                                  "Nrv2-GAL4 Control",
#                                                  "Nrv2-GAL4 > Lac RNAi"))
  
# Mdr65
# bio_confident_anno$genotype <- factor(bio_confident_anno$genotype, 
#                                       levels = c("Repo-GAL4 Control", 
#                                                  "Repo-GAL4 > Lac RNAi", 
#                                                  "Mdr65-GAL4 Control", 
#                                                  "Mdr65-GAL4 > Lac RNAi"))

# 46F
# bio_confident_anno$genotype <- factor(bio_confident_anno$genotype, 
#                                       levels = c("Repo-GAL4 Control", 
#                                                  "Repo-GAL4 > Lac RNAi", 
#                                                  "46F-GAL4 Control", 
#                                                  "46F-GAL4 > Lac RNAi"))

plot <- ggplot() +
  geom_path(data = bio_confident_anno, mapping = aes(x = x, y = y, group = larva_id, color = time)) +
  geom_circle(data = df, mapping = aes(x0 = centre_x, y0 = centre_y, r = radius)) +
  facet_wrap(~genotype) +
  ggtitle("Motion tracks of larval locomotion assay for Lac knockdown in motor neuron") +
  xlab("Distance (mm)") +
  ylab("Distance (mm)") +
  scale_color_gradientn(colors = plasma(100), name = "Time(s)") +
  theme_minimal() +
  theme(
    text = element_text(size = 8),
    plot.title = element_text(size = 8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.line = element_blank())+
  coord_fixed()

plot

ggsave("./Output/Plots/CH5_02092023_OK6_tracks_plasma.pdf", width = 7 * 0.7, height = 6 * 0.6, device = cairo_pdf)
```

# Get summary plots - all subtypes

# Import raw data for all subtypes
```{r}
perineurial <- qread("./Data/CH5_Crawling_assay_automated/46F_bio_confident_filtered.qs")
subperineurial <-qread("./Data/CH5_Crawling_assay_automated/Mdr65_bio_confident_filtered.qs")
wrapping <- qread("./Data/CH5_Crawling_assay_automated/Nrv2_bio_confident_filtered.qs")
motor_neuron <- qread("./Data/CH5_Crawling_assay_automated/OK6_bio_confident_filtered.qs")
```

# Process all data
```{r}
# Wrapping
bio_conf_wrap <- wrapping %>%
  mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
  mutate(genotype = case_when(
    str_detect(larva_id, "Nrv2") & str_detect(larva_id, "Control") ~ "Nrv2 Control",
    str_detect(larva_id, "Nrv2") & str_detect(larva_id, "GD") ~ "Nrv2>Lac RNAi",
    str_detect(larva_id, "Nrv2") & str_detect(larva_id, "KK") ~ "Nrv2 KK",
    str_detect(larva_id, "Repo") & str_detect(larva_id, "Control") ~ "Repo Control",
    str_detect(larva_id, "Repo") & str_detect(larva_id, "GD") ~ "Repo>Lac RNAi"
  )) %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  filter(genotype != "Nrv2 KK")

bio_summary_wrap <- perform_analysis(bio_conf_wrap) %>%
  distinct() %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  mutate(mean_speed_real_units = mean_speed * 85/1000)

# Subperineurial
bio_conf_sub <- subperineurial %>%
  mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
  mutate(genotype = case_when(
    str_detect(larva_id, "Mdr") & str_detect(larva_id, "control") ~ "Mdr65 Control",
    str_detect(larva_id, "Mdr") & str_detect(larva_id, "GD") ~ "Mdr65>Lac RNAi",
    str_detect(larva_id, "Mdr") & str_detect(larva_id, "KK") ~ "Mdr65 KK",
    str_detect(larva_id, "Repo") & str_detect(larva_id, "control") ~ "Repo Control",
    str_detect(larva_id, "Repo") & str_detect(larva_id, "GD") ~ "Repo>Lac RNAi"
  )) %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  filter(genotype != "Mdr65 KK")

bio_summary_sub <- perform_analysis(bio_conf_sub) %>%
  distinct() %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  mutate(mean_speed_real_units = mean_speed * 85/650)

# Perineurial
bio_conf_peri <- perineurial %>%
  mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
  mutate(genotype = case_when(
    str_detect(larva_id, "46F") & str_detect(larva_id, "control") ~ "46F Control",
    str_detect(larva_id, "46F") & str_detect(larva_id, "GD") ~ "46F>Lac RNAi",
    str_detect(larva_id, "46F") & str_detect(larva_id, "KK") ~ "46F KK",
    str_detect(larva_id, "Repo") & str_detect(larva_id, "control") ~ "Repo Control",
    str_detect(larva_id, "Repo") & str_detect(larva_id, "GD") ~ "Repo>Lac RNAi"
  )) %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  filter(genotype != "46F KK")

bio_summary_peri <- perform_analysis(bio_conf_peri) %>%
  distinct() %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  mutate(mean_speed_real_units = mean_speed * 85/1950)

# OK6
bio_confident_MN <- motor_neuron %>%
  mutate(larva_id = paste0(str_remove(filename, ".csv"), "_larva_", track_label)) %>%
  mutate(genotype = case_when(
    str_detect(larva_id, "OK6") & str_detect(larva_id, "CTRL") ~ "OK6 Control",
    str_detect(larva_id, "OK6") & str_detect(larva_id, "GD") ~ "OK6 > Lac RNAi",
    str_detect(larva_id, "OK6") & str_detect(larva_id, "KK") ~ "OK6 KK")) %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  filter(genotype != "OK6 KK")

bio_summary_MN <- perform_analysis(bio_confident_MN) %>%
  distinct() %>%
  mutate(replicate = str_extract(larva_id, "\\d")) %>%
  mutate(mean_speed_real_units = mean_speed * 85/650)
```

# Check n numbers
```{r}
bio_summary_repo %>%
  group_by(genotype) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```


# Filter for Repo and create Repo only dataframe
```{r}
filter_conditions <- function(df, suffix) {
  df %>% 
    filter(genotype %in% c("Repo Control", "Repo>Lac RNAi")) %>%
    mutate(larva_id = paste0(larva_id, suffix))
}

suffixes <- c("_peri", "_sub", "_wrap")
list_of_dfs <- list(bio_summary_peri, bio_summary_sub, bio_summary_wrap)

bio_summary_repo <- purrr::map2_dfr(list_of_dfs, suffixes, filter_conditions)
```

# Get combined statistics
```{r}
wrapping.df <- bio_summary_wrap %>%
  filter(!(genotype %in% c("Repo Control", "Repo>Lac RNAi")))

perineurial.df <- bio_summary_peri %>%
  filter(!(genotype %in% c("Repo Control", "Repo>Lac RNAi")))

subperineurial.df <- bio_summary_sub %>%
  filter(!(genotype %in% c("Repo Control", "Repo>Lac RNAi")))

process_dataframe <- function(df, control_group) {
  
  dev_area_cleaned <- df %>%
    pivot_longer(cols = c("mean_speed_real_units", "index_straightness", "DC", "SDDC"), names_to = "type") 

  dev_area_mean <- dev_area_cleaned %>%
    group_by(genotype, type) %>%
    summarise(
        mean = mean(value)
    ) %>%
    ungroup()

  dev_area_foldchange <- left_join(
    filter(dev_area_mean, genotype != control_group),
    filter(dev_area_mean, genotype == control_group) %>%
      dplyr::select(type, "control_mean" = mean),
    by = "type"
  ) %>%
    mutate(foldchange = mean / control_mean)

  dev_area_statistics <- dev_area_cleaned %>%
    group_by(type) %>%
    wilcox_test(value ~ genotype, ref.group = control_group) %>%
    dplyr::select(type, "condition" = group2, statistic, p, starts_with("n")) %>%
    left_join(dev_area_foldchange, by = c("type", "condition" = "genotype"))

  dev_area_statistics
}

list_of_dfs_for_combined <- list(perineurial.df, subperineurial.df, wrapping.df, bio_summary_repo, bio_summary_MN)
control_groups <- c("46F Control", "Mdr65 Control", "Nrv2 Control", "Repo Control", "OK6 Control")

combined_result <- purrr::map2_dfr(list_of_dfs_for_combined, control_groups, process_dataframe)
# write_csv(combined_result, "./Output/Crawling_assay_automated/statistical_results_all_crawling.csv")
```

```{r}
combined_result <- read_csv("./Output/Crawling_assay_automated/statistical_results_all_crawling.csv")
```

# Assign values for plotting
```{r}
crawling_statistics_for_plotting <- combined_result %>%
  mutate(
    p_numeric = p,  # preserve the original numeric p values
    p = case_when(
      p < 0.0001 ~ "**** < 0.0001",
      p < 0.001 ~ "*** < 0.001",
      p < 0.01 ~ "** < 0.01",
      p < 0.05 ~ "* < 0.05",
      TRUE ~ "N.S."
    )
  ) %>%
  mutate(type = case_when(
    type == "mean_speed_real_units" ~ "Crawling speed",
    type == "index_straightness" ~ "Path straightness",
    type == "DC" ~ "Movement linearity",
    type == "SDDC" ~ "Movement irregularity"
  )) %>%
  mutate(log2foldchange = log2(foldchange)) %>%
  mutate(p_label = str_c("p=", format(p_numeric, digits = 2, scientific = TRUE))) %>%  # use p_numeric here
  mutate(p_label_pos = case_when(
    log2foldchange >= 0 ~ log2foldchange + 0.08,
    log2foldchange < 0 ~ log2foldchange - 0.08
  ))

```

# Plot all to pdf
```{r}
colours <- c(sequential_hcl(n = 7, palette = "Inferno", rev = FALSE)[2:5], "gray70")

gene_order_dev <- crawling_statistics_for_plotting %>%
  filter(type == "Crawling speed") %>%
  arrange(desc(foldchange)) %>% pull(condition)

crawling_statistics_for_plotting %>%
  mutate(condition = fct_relevel(condition, gene_order_dev)) %>%
  ggplot(aes(x = condition, y = log2foldchange, fill = p)) + 
  geom_col(width = 0.6) +
  geom_hline(yintercept = 0, colour = "gray20", size = 0.1) +
  geom_text(aes(y = p_label_pos, label = p_label), cex = 1.4) +
  coord_cartesian()+
  # (ylim = c(-2.5, 1)) +
  labs(
    x = "", 
    y = "log2 Foldchange over Control",
    fill = "P-value"
  ) + 
  scale_fill_manual(values = colours) +
  facet_wrap(~ type) +
  theme_bw(base_size = 7) + 
  theme(
    legend.text = element_text(size = 5),
    legend.title = element_text(size = 5),
    axis.text.x = element_text(size = 3.5)
    ) +
  guides(fill = guide_legend(keywidth = 0.3, keyheight = 0.3)) -> dev_plot

dev_plot
# Save figure
ggsave("./Output/Plots/CH5_17092023_subtypes_crawling_combined.pdf",
       width = 11 * 0.3937, height = 8 * 0.38937,
       device = cairo_pdf)
```

