---
title: "NMJ_data_analysis_smFISH_neuron_glia_area"
output: html_document
editor_options: 
  chunk_output_type: console
---

# R ENVIRONMENT 

```{r}
library(tidyverse)
library(patchwork)
library(rstatix)
library(ggpubr)
library(stringr)
`%!in%` = Negate(`%in%`)
options(scipen = 999)
```

# ANALYSIS

# Import area of lac::YFP data
```{r}
file_list = list.files(path ="./Data/CH5_Lac_YFP_KStim_smFISH/Areas_of_glia_neuron/Areas_intensity_glia/CSVs/", 
                       pattern = "*.csv", 
                       full.names = TRUE)

df <- map_df(file_list, ~ read_csv(.x, col_names = TRUE) %>%
                             mutate(name = str_remove_all(basename(.x), ".csv")))
```

# Import area of neuron data
```{r}
file_list = list.files(path ="./Data/CH5_Lac_YFP_KStim_smFISH/Areas_of_glia_neuron/Areas_HRP/CSVs/", 
                       pattern = "*.csv", 
                       full.names = TRUE)

df_HRP <- map_df(file_list, ~ read_csv(.x, col_names = TRUE) %>%
                             mutate(name = str_remove_all(basename(.x), ".csv")))
```

# Import background information data (for Lac::YFP protein density only)
```{r}
bg_subtraction_df <- read_csv("./Data/CH5_Lac_YFP_KStim_smFISH/KStim_BG_channel_Lac.csv")

bg_df_intensities <- bg_subtraction_df %>%
  mutate(bg_density = RawIntDen/Area)

mean_bg_density <- mean(bg_df_intensities$bg_density)
```

# Clean area data - Lac::YFP
```{r}
clean <- df %>%
  group_by(name) %>%
  summarise(sum_Area = sum(Area), sum_RawIntDen = sum(RawIntDen)) %>%
  ungroup() %>%
    mutate(condition = case_when(
    str_detect(name, "_stim_") ~ "Stimulated",
    str_detect(name, "unstim_mock") ~ "Mock stimulated",
    str_detect(name, "unstim_open") ~ "Unstimulated")) %>%
    filter(condition != "Mock stimulated") %>%
  mutate(density = ((sum_RawIntDen-(mean_bg_density*sum_Area))/sum_Area))
```

# Create clean df with density info and correct labels
```{r}
long_df <- clean %>%
  gather(key = "measure", value = "value", sum_Area, density) %>%
  mutate(measure = recode(measure,
                          sum_Area = "Area (um^2)",
                          density = "Lac::YFP signal density (A.U.)"))
```

#Check if normal
```{r}
clean %>%
  group_by(condition) %>%
  shapiro_test(density) %>%
  add_significance()

clean %>%
  group_by(condition) %>%
  shapiro_test(sum_Area) %>%
  add_significance()
```

# Run stats
```{r}
stats_density <- clean %>%
  wilcox_test(density ~ condition) %>%
  add_significance()

stats_area <- clean %>%
  wilcox_test(sum_Area ~ condition) %>%
  add_significance()
```

# Plot area and density data for Lac::YFP
```{r}
long_df$condition <- factor(long_df$condition, levels = c("Unstimulated","Stimulated"))

# Custom labeller function
label_math <- function(variable,value){
  return(list(
    "Area (um^2)" = expression(paste("Area (", mu, m^2, ")", sep = "")),
    "Lac::YFP signal density (A.U.)" = "Lac::YFP signal density (A.U.)"
  )[value])
}

# Your ggplot code
ggplot(long_df, aes(x = condition, y = value)) +
  geom_jitter(width = 0.1, alpha = 0.3, size = 2) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.45, size = 0.7, color = "#C53270") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "#C53270", size = 1) +
  stat_compare_means(comparisons = list(c("Unstimulated", "Stimulated")), method = "wilcox.test", label = "p.signif") +
  facet_wrap(~ measure, scales = "free_y", labeller = label_math) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))+
  labs(x = NULL,
       title = "Lac::YFP area and protein signal intensity comparison",
       y = NULL)

## Save
# ggsave("/Users/daliagala/Library/CloudStorage/OneDrive-Nexus365/Thesis/Scripts/Output/Plots/Lac_YFP_KStim_lac_area_density.pdf",
#        width = 10 * 0.5, height = 10 * 0.5,
#        device = cairo_pdf)
```

# Clean area data - neuron
```{r}
clean_HRP <- df_HRP %>%
  group_by(name) %>%
  summarise(sum_Area = sum(Area)) %>%
  ungroup() %>%
    mutate(condition = case_when(
    str_detect(name, "_stim_") ~ "Stimulated",
    str_detect(name, "unstim_mock") ~ "Mock stimulated",
    str_detect(name, "unstim_open") ~ "Unstimulated")) %>%
    filter(condition != "Mock stimulated")
```

#Check if normal
```{r}
clean_HRP %>%
  group_by(condition) %>%
  shapiro_test(sum_Area) %>%
  add_significance()
```

# Run stats
```{r}
stats_HRP <- clean_HRP %>%
  t_test(sum_Area ~ condition) %>%
  add_significance()
```

# Plot area data for Lac::YFP HRP areas
```{r}
clean_HRP$condition <- factor(clean_HRP$condition, levels = c("Unstimulated", "Stimulated"))

ggplot(clean_HRP, aes(x = condition, y = sum_Area)) +
  geom_jitter(width = 0.1, alpha = 0.3, size = 4) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.45, size = 0.7, color = "#C53270") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "#C53270", size = 1) +
  stat_compare_means(comparisons = list(c("Unstimulated", "Stimulated")), method = "wilcox.test", label = "p.signif") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(plot.title = element_text(size = 14),
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(size = 10))+
  labs(x = NULL,
       title = "Lac::YFP axon projection area comparison",
       y = expression(paste("Area (",mu, m^2,")",sep="")))

# ggsave("/Users/daliagala/Library/CloudStorage/OneDrive-Nexus365/Thesis/Scripts/Output/Plots/Lac_YFP_KStim_lac_area.pdf",
#        width = 10 * 0.5, height = 10 * 0.5,
#        device = cairo_pdf)
```
