---
title: "NMJ_analysis_smFISH_spots_whole_NMJ_lac"
output: html_document
editor_options: 
  chunk_output_type: console
---

# R ENVIRONMENT 

```{r}
library(tidyverse)
library(patchwork)
library(rstatix)
library(ggpubr)
library(stringr)
`%!in%` = Negate(`%in%`)
options(scipen = 999)
```

# ANALYSIS

# Import smFISH molecules in glial cells data
```{r}
dataframe <- read_csv("./BigFISH_pypeline/final_results_KStim_Lac_YFP_smFISH_Lac_Area.csv")

clean_glial_molecules <- dataframe %>%
  mutate(condition = case_when(
    str_detect(Filename, "_stim_") ~ "Stimulated",
    str_detect(Filename, "unstim_open") ~ "Unstimulated")) %>%
  rename("Lac::YFP Area" = "Common Coordinates") %>%
  mutate(Filename = gsub("^ROI_", "", Filename)) %>%
  mutate(Filename = gsub("_C2_cropped.tif", "", Filename))
```

# Import Lac::YFP area data
```{r}
file_list_glia = list.files(path = "./Data/CH5_Lac_YFP_KStim_smFISH/Areas_of_glia_neuron/Areas_intensity_glia/CSVs/",
                       pattern = "*.csv",
                       full.names = TRUE)

df_glia <- map_df(file_list_glia, ~ read_csv(.x, col_names = TRUE) %>%
                             mutate(Filename = str_remove_all(basename(.x), ".csv")))
df_glia$Label = NULL
df_glia$...1 = NULL
```

# Clean Lac::YFP area dataframe
```{r}
areas_glia_clean <- df_glia %>%
  group_by(Filename) %>%
  summarise("Lac_YFP_Area" = sum(Area)) %>%
  ungroup() %>%
  mutate(
    Filename = gsub("^Results_AreaROI_MAX_", "", Filename)) %>%
  mutate(condition = case_when(
    str_detect(Filename, "_stim_") ~ "Stimulated",
    str_detect(Filename, "unstim_open") ~ "Unstimulated",
    str_detect(Filename, "mock") ~ "Mock", )) %>%
  filter(condition != "Mock")

areas_glia_clean$condition = NULL
```

# 
```{r}
glia <- merge(clean_glial_molecules,
              areas_glia_clean[, c("Filename", "Lac_YFP_Area")],
              by = "Filename",
              all.x = TRUE)
glia <- glia %>%
  mutate(mol_per_area = `Lac::YFP Area`/Lac_YFP_Area)

summary <- glia %>%
  group_by(condition) %>%
  summarise(
    area_means = mean(`Lac_YFP_Area`, na.rm = TRUE),
    molecules_means = mean(`Lac::YFP Area`, na.rm = TRUE)
  )
```

```{r}
glia %>%
  group_by(condition) %>%
  shapiro_test(mol_per_area) %>%
  add_significance()
```

```{r}
glia %>%
  wilcox_test(mol_per_area ~ condition) %>%
  add_significance()
```

# Import smFISH molecules in neuron data
```{r}
dataframe <- read_csv("./BigFISH_pypeline/final_results_KStim_Lac_YFP_smFISH_Neuron.csv")

clean_neuron_molecules <- dataframe %>%
  rename("α-HRP Area" = "Common Coordinates") %>%
  mutate(Filename = gsub("^ROI_", "", Filename)) %>%
  mutate(Filename = gsub("_C3_cropped.tif", "", Filename))
```

# Import neuronal area data
```{r}
file_list_neuron = list.files(path = "./Data/CH5_Lac_YFP_KStim_smFISH/Areas_of_glia_neuron/Areas_HRP/CSVs/",
                       pattern = "*.csv",
                       full.names = TRUE)

df_neuron <- map_df(file_list_neuron, ~ read_csv(.x, col_names = TRUE) %>%
                             mutate(Filename = str_remove_all(basename(.x), ".csv")))
df_neuron$Label = NULL
df_neuron$...1 = NULL
```

# Clean HRP data
```{r}
areas_neuron_clean <- df_neuron %>%
  group_by(Filename) %>%
  summarise("Neuron Area" = sum(Area)) %>%
  ungroup() %>%
  mutate(
    Filename = gsub("^Results_AreaROI_MAX_", "", Filename)) %>%
  mutate(condition = case_when(
    str_detect(Filename, "_stim_") ~ "Stimulated",
    str_detect(Filename, "unstim_open") ~ "Unstimulated",
    str_detect(Filename, "mock") ~ "Mock", )) %>%
  filter(condition != "Mock")

areas_neuron_clean$condition = NULL
```

# Merge neuronal with glial molecules, get stats
```{r}
result_molecules <- merge(clean_glial_molecules,
                          clean_neuron_molecules[, c("Filename", "α-HRP Area")],
                          by = "Filename",
                          all.x = TRUE)

longer_molecules <- result_molecules %>%
  gather(key = "Original_Column", value = "no_mRNA_molecules", "Lac::YFP Area", "α-HRP Area")

longer_molecules %>%
  group_by(condition, Original_Column) %>%
  shapiro_test(no_mRNA_molecules) %>%
  add_significance()

longer_molecules %>%
  group_by(condition) %>%
  wilcox_test(no_mRNA_molecules ~ Original_Column, p.adjust.method = "bonferroni") %>%
  add_significance()
```

# Merge neuronal with glial areas
```{r}
result_areas <- merge(areas_glia_clean,
                          areas_neuron_clean[, c("Filename", "Neuron Area")],
                          by = "Filename",
                          all.x = TRUE)
```

# Ratios
```{r}
result <- merge(result_molecules,
                result_areas[, c("Filename", "Lac_YFP_Area", "Neuron Area")],
                by = "Filename",
                all.x = TRUE)

result_annotated <- result %>%
  mutate(mols_per_neuron = `α-HRP Area`/`Neuron Area`) %>%
  mutate(mols_per_Lac = `Lac::YFP Area`/Lac_YFP_Area) %>%
  mutate(Lac_to_axon_ratio_mols = (`Lac::YFP Area`/`α-HRP Area`)*100) %>%
  mutate(Lac_to_axon_ratio_areas = (Lac_YFP_Area/`Neuron Area`)*100)

df_longer <- result_annotated %>%
  gather(key = "Original_Column", value = "Value", Lac_to_axon_ratio_mols:Lac_to_axon_ratio_areas)
```

# Get stats for area/mol ratio vs stim unstim condition
```{r}
result_annotated %>%
  group_by(condition) %>%
  shapiro_test(Lac_to_axon_ratio_areas) %>%
  add_significance()

result_annotated %>%
  wilcox_test(Lac_to_axon_ratio_areas ~ condition) %>%
  add_significance()
```

# Get stats for stim unstim condition vs area/mol ratio
```{r}
df_longer %>%
  group_by(condition, Original_Column) %>%
  shapiro_test(Value) %>%
  add_significance()

df_longer %>%
  group_by(condition) %>%
  wilcox_test(Value ~ Original_Column, p.adjust.method = "bonferroni") %>%
  add_significance() -> stats
```

# Plot ratios vs stim unstim condition
```{r}
custom_labels <- c("Area ratio (Lac::YFP/HRP)", "Lac mRNA molecules ratio")
# Organise factor
df_longer$condition <- factor(df_longer$condition, levels = c("Unstimulated", "Stimulated"))

ggplot(df_longer, aes(x = Original_Column, y = Value)) +
  geom_jitter(width = 0.1, alpha = 0.3, size = 2) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.45, size = 0.6, color = "#C53270") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "#C53270", size = 1) +
  stat_compare_means(comparisons = list(c("Lac_to_axon_ratio_areas", "Lac_to_axon_ratio_mols")), method = "t.test", label = "p.signif") +
  theme_classic2() +
  facet_wrap(~ condition)+
  scale_x_discrete(labels = custom_labels)+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(plot.title = element_text(size = 12),
        axis.title.y = element_text(size = 8),
        axis.text.x = element_text(size = 6))+
  labs(x = NULL,
       title = "Lac mRNA molecules in motor neuron terminal and Lac::YFP area",
       y = "Ratio of measure in Lac::YFP area to motor neuron terminal area (%)")

ggsave("./Output/Plots/Lac_YFP_Lac_mRNA_ratios_glia_Neuron.pdf",
       width = 15 * 0.38937, height = 10 * 0.38937,
       device = cairo_pdf)

```


```{r}
# Organise factor
glia$condition <- factor(glia$condition, levels = c("Unstimulated", "Stimulated"))

ggplot(glia, aes(x = condition, y = mol_per_area)) +
  geom_jitter(width = 0.1, alpha = 0.3, size = 4) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.45, size = 0.6, color = "#C53270") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "#C53270", size = 1) +
  stat_compare_means(comparisons = list(c("Unstimulated", "Stimulated")), method = "t.test", label = "p.signif") +
  theme_classic2() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(plot.title = element_text(size = 10),
        axis.title.y = element_text(size = 8),
        axis.text.x = element_text(size = 8))+
  labs(x = NULL,
       title = "Lac::YFP mRNA molecules per unit of Lac::YFP area",
       y = expression(paste("Lac::YFP mRNA molecules per 1 (",mu, m^2,")",sep="")))

ggsave("./Output/Plots/Lac_YFP_Lac_mRNA_Kstim_mol_per_area.pdf",
       width = 10 * 0.38937, height = 10 * 0.38937,
       device = cairo_pdf)
```

# Pivot longer for plotting compartment
```{r}
long <- result_neuron_glia %>% 
  pivot_longer(
    cols = c("α-HRP Area", "Lac::YFP Area"),
    names_to = "compartment",
    values_to = "no_mRNA_molecules"
)
```

#Check if normal - glia only
```{r}
long %>%
  group_by(condition, compartment) %>%
  shapiro_test(no_mRNA_molecules) %>%
  add_significance()
```

# Calculate statistics - glia only
```{r}
stats <- long %>%
  group_by(compartment) %>%
  wilcox_test(no_mRNA_molecules ~ condition, p.adjust.method = "bonferroni") %>%
  add_significance()
```

# Plot - Lac::YFP mRNA molecules vs compartment
```{r}
# Organise factor
long$condition <- factor(long$condition, levels = c("Unstimulated", "Stimulated"))

ggplot(long, aes(x = condition, y = no_mRNA_molecules)) +
  geom_jitter(width = 0.1, alpha = 0.3, size = 4) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.45, size = 0.6, color = "#C53270") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "#C53270", size = 1) +
  stat_compare_means(comparisons = list(c("Unstimulated", "Stimulated")), method = "wilcox.test", label = "p.signif") +
  theme_classic2() +
  facet_wrap(~ compartment) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(plot.title = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 8))+
  labs(x = NULL,
       title = "Lac::YFP mRNA molecules in different NMJ compartments",
       y = "Number of Lac::YFP mRNA molecules")


ggsave("./Output/Plots/CH5_Lac_RNAi_KStim_mRNA_NMJ_compartments.pdf",
       width = 10 * 0.4, height = 10 * 0.4,
       device = cairo_pdf)
```

# Plot - Lac::YFP mRNA molecules vs condition
```{r}
# Organise factor
long$compartment <- factor(long$compartment, levels = c("Lac::YFP Area", "α-HRP Area"))

ggplot(long, aes(x = compartment, y = no_mRNA_molecules)) +
  geom_jitter(width = 0.1, alpha = 0.3, size = 4) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.45, size = 0.6, color = "#C53270") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "#C53270", size = 1) +
  stat_compare_means(comparisons = list(c("Lac::YFP Area", "α-HRP Area")), method = "wilcox.test", label = "p.signif") +
  theme_classic2() +
  facet_wrap(~ condition) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(plot.title = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 8))+
  labs(x = NULL,
       title = "Lac::YFP mRNA molecules before and after potassium stimulation",
       y = "Number of Lac::YFP mRNA molecules")


ggsave("./Output/Plots/CH5_Lac_RNAi_KStim_mRNA_NMJ_pre_post_stim.pdf",
       width = 10 * 0.4, height = 10 * 0.4,
       device = cairo_pdf)
```

# Get proportions of molecules
```{r}
result_neuron_glia<- 
  result_neuron_glia %>%
  mutate(ratio = (`Lac::YFP Area`/`α-HRP Area`)*100)
```

# Plot ratio
```{r}
# Organise factor
result_neuron_glia$condition <- factor(result_neuron_glia$condition, levels = c("Unstimulated", "Stimulated"))

ggplot(result_neuron_glia, aes(x = condition, y = ratio)) +
  geom_jitter(width = 0.1, alpha = 0.3, size = 4) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.45, size = 0.6, color = "#C53270") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "#C53270", size = 1) +
  stat_compare_means(comparisons = list(c("Unstimulated", "Stimulated")), method = "wilcox.test", label = "p.signif") +
  theme_classic2() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  theme(plot.title = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 8))+
  labs(x = NULL,
       title = "Ratios of Lac mRNA molecules in Lac::YFP to α-HRP areas",
       y = "Number of Lac::YFP mRNA molecules")


ggsave("./Output/Plots/CH5_Lac_RNAi_KStim_mRNA_NMJ_ratios_pre_post_stim.pdf",
       width = 10 * 0.4, height = 10 * 0.4,
       device = cairo_pdf)
```

